\LARGE \bf Object Detection-Based Behaviour using Deep-Learning on Thymio

### 2018-06-01 paper/paper.tex
latest changes to the paper

Specifically, our robot will wait for a user-specified class, e.g. \emph{dog}, and, when found, it moves towards the object by keeping it in the middle of its view. We also implemented a PID-based algorithm to avoid obstacles and properly stop in front of the founded item.

@@

\includegraphics[width=0.25\linewidth]{images/leds/1}	
\includegraphics[width=0.25\linewidth]{images/leds/2}	
\includegraphics[width=0.25\linewidth]{images/leds/3}	
\end{center}
\begin{center}
\includegraphics[width=0.25\linewidth]{images/leds/4}	
\includegraphics[width=0.25\linewidth]{images/leds/5}
\end{center}
\caption{On board LEDs}
\end{figure}
A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found at

\section{Conclusion}
In this paper, we presented a light and scalable architecture that uses a real-time Object Detection model to correctly find objects in the surrounding environment and to perform actions based on them. Moreover, because the only  hardware constraint is the camera, our work can be used into similar robots running ROS  to extend their functionalities. Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain. This symbiosis between Machine Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.

>>>>

Specifically, our robot will wait for a user-specified class, e.g. \emph{dog}, and, when it finds it using the object detecttion model on the camera image, it moves towards the object by keeping it in the middle of its view. We also implemented a PID-based algorithm to avoid obstacles and properly stop in front of the founded item.

@@

\includegraphics[width=0.25\linewidth]{images/leds/1}	
\includegraphics[width=0.25\linewidth]{images/leds/2}	
\includegraphics[width=0.25\linewidth]{images/leds/3}	
\end{center}
\begin{center}
\includegraphics[width=0.25\linewidth]{images/leds/4}	
\includegraphics[width=0.25\linewidth]{images/leds/5}
\end{center}
\caption{On board LEDs}
\end{figure}
A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found \href{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}{here}\footnote{\texttt{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}}, and the third person view \href{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}{here}\footnote{\texttt{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}}.
\section{Conclusion}
In this paper, we presented a light and scalable architecture that uses a real-time Object Detection model to correctly find objects in the surrounding environment and to perform actions based on them. Moreover, because the only  hardware constraint is the camera, our work can be used into similar robots running ROS  to extend their functionalities. Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain. This symbiosis between Deep Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.
